MLH1 Results Outline

### 2020-04-23 doc/Results_v2.rmd
making table, changing L and Z  to early and late

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(ggplot2)
#library(pwr)
library(plyr)
library(lattice)
library(dplyr)
library(raster)
library(lme4)
library(nlme)
library(RLRsim)
library(ggpubr)
library(reshape2)
#library(patchwork)

@@

@@

                 ncells = length(fileName),
                 mean.count = mean( total.count)
)
DMC1.mean.obs.L$stage <- "L"

DMC1.mean.obs.Z <- ddply(.data=DMC1.DF[DMC1.DF$stage == "Z",],
                 .(category),
                 summarize, 
                 ncells = length(fileName),
                 mean.count = mean( total.count)
)
DMC1.mean.obs.Z$stage <- "Z"

@@

#write.table(DMC1.mean.table, "~./MLH1repo/DMC1.mean.table.csv", sep=",",
#            row.names = FALSE)

@@

```{r MAIN.DMC1.plot, echo=FALSE, warning=FALSE}
#think of better color scheme
#make the jitter col thinner or make the stacked dots.
#remember that box-plots add outlier dots.
#change y labels

@@

```{r plot.t.test, echo=FALSE, include=FALSE}

  #this will add neat bars, but still need to figure out what groups ect it's actually using
#THE stat_compare function adds a arm thing and pvalue for 
#  stat_compare_means(comparisons = my_comparisons)

#status - legend, expression y-axis, facet, facet_wrap SYMBOL
#legend - stage. y=total count, FACet strain

#add column to distinguish high vs low rec strains
DMC1.DF$rec_group <- ifelse(grepl("WSB", DMC1.DF$strain), "Low",
                          ifelse(grepl("G",DMC1.DF$strain), "Low",

              ifelse(grepl("KAZ", DMC1.DF$strain), "Low",
            ifelse(grepl("PWD", DMC1.DF$strain), "High",
               ifelse(grepl("MSM", DMC1.DF$strain), "High","")))))

DMC1.DF$rec_group <- as.factor(DMC1.DF$rec_group)

# annotation table with adjusted pvals and y-position of the labels

anno_df = compare_means(total.count ~ rec_group, group.by = "stage", data = DMC1.DF[DMC1.DF$stage != "P",],method = "t.test") %>% mutate(y_pos = 300)
#

DMC1.bxlt_High.to.Low <- ggplot(DMC1.DF[DMC1.DF$stage != "P",], aes(x=rec_group, y=total.count)) + 
  geom_boxplot(position=position_dodge()) + 
  geom_point(aes(color=stage), position=position_jitterdodge()) + 
  facet_wrap(~stage, nrow=1) + 
  ggsignif::geom_signif(
    data=anno_df, 
    aes(xmin=group1, xmax=group2, annotations=p.adj, y_position=y_pos), 
    manual=TRUE
  )+ggtitle("Comparison of DMC1 means across high and low recombing groups")+theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

#example for ggplot+ test from here
#https://github.com/kassambara/ggpubr/issues/65

#https://www.r-bloggers.com/add-p-values-and-significance-levels-to-ggplots/

@@

```{r DMC1_anova, echo=FALSE, warning=FALSE}
#1. ANOVA, is there a difference in DMC1 counts across strains?

#unorder strain
DMC1.DF$strain <- factor(DMC1.DF$strain, levels = c("G","WSB","KAZ","PWD","MSM"), ordered = FALSE )

mod.L <- lm(total.count ~ strain, data = DMC1.DF[DMC1.DF$stage == "L",])
mod.Z <- lm(total.count ~ strain, data = DMC1.DF[DMC1.DF$stage == "Z",])

l.anova.pval <- anova(mod.L)$`Pr(>F)`[1] #0.0002701 ***
z.anova.pval <- anova(mod.Z)$`Pr(>F)`[1] #NS

#anova's aren't appropriate for 2 samples... re-do the anova
#so that it's compareing more than just 2 categories -- or delete

```{r DMC1_MLH1.MAIN_TABLE, echo=FALSE, warning = FALSE}
#make category averages from AP_mouse_table.HQ
mean.MLH1.obs <- ddply(.data=AP_mouse_table.HQ,
                 .(category),
                 summarize, 
                 mean.MLH1 = mean(mean_co),
                 var.MLH1 = var(mean_co)
)

DMC1.target.strains <- subset(mean.MLH1.obs, category == "G male" |
                   category == "WSB male" |
                     category == "KAZ male" |
                  category == "MSM male" |
                    category == "PWD male")
#attach this mini DF to the DMC1 data

DMC1.mean.obs.L$mean.count.L <- DMC1.mean.obs.L$mean.count
DMC1.mean.obs.Z$mean.count.Z <- DMC1.mean.obs.Z$mean.count

@@

#colnames(DMC1table.main) <- c("category", "mean.MLH1", "", "", "")

#DMC1.mean.table
DMC1.mean.table.99 <- subset(DMC1table.main, select= -c(var.MLH1,  mean.count.x,  mean.count.y, stage.x, stage.y))

colnames(DMC1.mean.table.99) <- c("category","mean.MLH1","ncells.L","mean.L",
                  "ncells.Z", "mean.Z", "MLH1.L_ratio", "MLH1.Z_ratio")

WSB_DMC1.Z_CO_ratio <-   ( DMC1table.main %>% filter(category == "WSB male") )$mean.count.L / (DMC1table.main %>% filter(category == "WSB male"))$mean.MLH1

@@

#MAIN TABLE, headers need to be fixed, remove var.MLH1
#try adding double decker colume names / lines for early Z and late Z
#kable(head(DMC1table.main),  caption = "Table X. DMC1 foci counts per cell summary")

@@

@@

```{r with.cow, echo=FALSE, warning=FALSE}
library(cowplot)

@@

plot_grid(top.triangle, bottom.triangle, align = "v", rel_widths = c(1.3, 1.3))

>>>>

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(kableExtra)
library(ggplot2)
#library(pwr)
library(plyr)
library(lattice)
library(dplyr)
library(raster)
library(lme4)
library(nlme)
library(RLRsim)
library(ggpubr)
library(reshape2)
#library(patchwork)

@@

- update figure

- make table, save in figure folder, print head here

- remove cody blocks

@@

                 ncells = length(fileName),
                 mean.count = mean( total.count)
)
DMC1.mean.obs.L$stage <- "early Z"

DMC1.mean.obs.Z <- ddply(.data=DMC1.DF[DMC1.DF$stage == "Z",],
                 .(category),
                 summarize, 
                 ncells = length(fileName),
                 mean.count = mean( total.count)
)
DMC1.mean.obs.Z$stage <- "late Z"

@@

@@

```{r MAIN.DMC1.plot, echo=FALSE, warning=FALSE}
DMC1.DF$stage

@@

@@

```{r DMC1_MLH1.MAIN_TABLE, echo=FALSE, warning = FALSE}

@@

#colnames(DMC1table.main) <- c("category", "mean.MLH1", "", "", "")
WSB_DMC1.Z_CO_ratio <-   ( DMC1table.main %>% filter(category == "WSB male") )$mean.count.L / (DMC1table.main %>% filter(category == "WSB male"))$mean.MLH1

@@

@@

```{r DMC1.table, echo=FALSE}

#make category averages from AP_mouse_table.HQ
mean.MLH1.obs <- ddply(.data=AP_mouse_table.HQ,
                 .(category),
                 summarize, 
                 mean.MLH1 = mean(mean_co),
                 var.MLH1 = var(mean_co)
)

DMC1.target.strains <- subset(mean.MLH1.obs, category == "G male" |
                   category == "WSB male" |
                     category == "KAZ male" |
                  category == "MSM male" |
                    category == "PWD male")
#attach this mini DF to the DMC1 data
DMC1.mean.obs.L$mean.count.L <- DMC1.mean.obs.L$mean.count
DMC1.mean.obs.Z$mean.count.Z <- DMC1.mean.obs.Z$mean.count

#DMC1.mean.table
DMC1table.main99 <- subset(DMC1table.main, select= -c(stage.x, var.MLH1, stage.y, mean.count.x, mean.count.y))

DMC1table.main99 <-  DMC1table.main[, c("category","mean.MLH1","ncells.x","mean.count.L", "MLH1.L_ratio", "ncells.y","mean.count.Z", "MLH1.Z_ratio"),  drop=FALSE]

colnames(DMC1table.main99) <- c("category", "mean MLH1",    "ncells",     "mean DMC1", "MLH1:DMC1 ratio", "ncells",     "mean DMC1", "MLH1:DMC1 ratio")

kable(DMC1table.main99, row.names = F) %>%
  kable_styling() %>%
  add_header_above(c(" " = 2, "Early Zygotene" = 3, "Late Zygotene" = 3)) %>%
  scroll_box(width = "800px", height = "200px")
```

@@

```{r with.cow, echo=FALSE, warning=FALSE, message=FALSE}
library(cowplot)

@@

#plot_grid(top.triangle, bottom.triangle, align = "v", rel_widths = c(1.3, 1.3))

```{r another.triangle, echo=FALSE, fig.width = 5, fig.height=5}

Curated_BivData <- Curated_BivData %>% filter(PER_Foci_2 < 1.01)

with( (Curated_BivData %>% filter(strain == "G") ), { 
  plot(  c( (Curated_BivData %>% filter(sex == "male") %>% filter(strain == "G") %>% filter(hand.foci.count == 2))$PER_Foci_2,
              (Curated_BivData %>% filter(strain == "G") %>% filter(sex == "female") %>% filter(hand.foci.count == 2))$PER_Foci_1),

                     c(   (Curated_BivData %>% filter(sex == "male") %>% filter(strain == "G") %>% filter(hand.foci.count == 2) )$PER_Foci_1,

                       (Curated_BivData %>% filter(strain == "G") %>% filter(sex == "female") %>% filter(hand.foci.count == 2) )$PER_Foci_2), 
          xlab = "Position1", ylab = "Position2", asp = 1, main="G IFD distributions"); 
  axis(4, las = 1, pos=1); #right side
  axis(side = 3, las = 1, pos=1); #
  segments(0, 0, 1, 1); abline(v = 0:1, h = 0:1) })

reverse the axis
